Article Title

### 2013-09-26 sections/Results.tex

\subsection*{Regularized estimates of the covariance matrix}
To assess the quality of a covariance matrix estimate $\hat\Sigma$, we must define a real-valued \emph{loss function} $\mathcal L(\hat\Sigma,\Sigma)$, which attains its minimum when $\hat\Sigma = \Sigma$. For the purposes of this study, we adopted the \emph{Gaussian loss} function:
\begin{equation}
\mathcal L(\hat\Sigma,\Sigma) = \mathcal L_g(\hat\Sigma,\Sigma) = \frac 1 p(\ln \det \hat \Sigma + \Tr(\hat \Sigma^{-1}\Sigma))
\end{equation}
which resembles the negative multivariate normal log-likelihood (see Appendix).

Although the sample covariance matrix is unbiased: $\mathbb E[\hat\Sigma_0]=\Sigma$, it is not as close to $\Sigma$ as possible, on average. We must seek  to minimize the expected value of the loss function, known as \emph{estimator risk} 
\begin{equation}
r = \mathbb E[\mathcal L(\hat\Sigma, \Sigma)]
\end{equation}

>>>>

\subsection*{Regularized estimates of the covariance matrix}
To assess the quality of a covariance matrix estimate $\hat\Sigma$, we must define a real-valued \emph{loss function} $\mathcal L(\hat\Sigma,\Sigma)$, which attains its minimum when $\hat\Sigma = \Sigma$. For the purposes of this study, we adopted the \emph{negative normal log-likelihood loss} function (see Appendix for details):
\begin{equation}
\mathcal L(\hat\Sigma,\Sigma) = \frac 1 p\left[\ln \det \hat \Sigma + \Tr(\hat \Sigma^{-1}\Sigma)\right]
\end{equation}

We seek an estimate of the covariance matrix that minimizes the expected value of loss, referred to as \emph{estimator risk}: 
\begin{equation}
r = \mathbb E[\mathcal L(\hat\Sigma, \Sigma)]
\end{equation}

The sample covariance matrix is unbiased: it minimizes the bias $\mathcal L (\mathbb E[\hat\Sigma],\Sigma)$ but it does
